Analytical Model for the Current Density in the Electrochemical Synthesis of Porous Silicon Structures with a Lateral Gradient

### 2020-12-22 paper.tex
Add corrections about linear fit.

From the data in Table \ref{t:jpdv} we can plot the fitted porosity as
a function of the calculated density current, as shown for our three
samples in Fig. \ref{fig:p}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{pvsj}
  \caption{Porosity as a function of current density for three samples
    $S_1$, $S_2$, $S_3$. The data points for each sample are joined by
    thick lines. The arrows point to data that correspond to
    position $x'_1=0.2\,\text{cm}$, joined to the other data by thin
    lines (see text). We include linear fits to the data from
    sample $S_3$ (thick straight line) and to that from all the
    samples (thin straight line). }
  \label{fig:p}
\end{figure}
Notice that for each sample the data points lie around straight lines,
except for one outlier point in each corresponding to position
$x'_1$. As discussed in Sec. \ref{sec:ps-grin-single}, those points
were very close to a wall of the electrolytic cell, so they were
affected by leakage currents towards the underside of the wall.
For this reason, we exclude those points from the following
analysis. We made a linear fit to the data from sample $S_3$ and to
the data from the three samples. A comparison shows that a fit to the
data of just one sample, $S_3$, turns out to be a reasonable predictor for the
porosity of all the samples.  From that fit we obtain that for our
preparation conditions
\begin{equation}\label{eq:p}
  p\approx 0.013\frac{\text{cm}^2}{\text{mA}} j_\perp+0.53.
\end{equation}
The discrepancies may be due to the ill definition of the edge of the
sample (the position of the sealing o-ring) with respect to which we
measured the position of the illuminating spot. A rigid displacement along
$x$ yields mostly a horizontal shift of the results shown in
Fig. \ref{fig:p} and that can bring them into closer agreement.

>>>>

From the data in Table \ref{t:jpdv} we can plot the fitted porosity vs.
the calculated density current, as shown for our three
samples in Fig. \ref{fig:p}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{pvsj}
  \caption{Porosity vs. current density for the three samples
    $S_1$, $S_2$, $S_3$. The data points for each sample are joined by
    thick lines. The arrows point to data that correspond to
    position $x'_1=0.2\,\text{cm}$, joined to the other data by thin
    lines (see text). We include linear fits of the form
    $p=mj_\perp+b$ to the data from
    sample $S_3$ (thick straight line, with parameters $m=0.0134$ and
    $b=0.5288$) and to that from all the samples (thin straight line). }
  \label{fig:p}
\end{figure}
Notice that for each sample the data points lie around straight lines,
except for one outlier point in each corresponding to position
$x'_1$. As discussed in Sec. \ref{sec:ps-grin-single}, those points
were very close to a wall of the electrolytic cell, so they were
affected by leakage currents towards the underside of the wall.
For this reason, we exclude those points from the following
analysis. We made a linear fit of the form $p=mj_\perp+b$ to the data from sample $S_3$ and to
the data from the three samples. A comparison shows that a fit to the
data of just one sample, $S_3$, turns out to be a reasonable predictor for the
porosity of all the samples.  From that fit we obtain that for our
preparation conditions
\begin{equation}\label{eq:p}
  p\approx 0.013\frac{\text{cm}^2}{\text{mA}} j_\perp+0.53.
\end{equation}
The discrepancies may be due to the ill definition of the edge of the
sample (the position of the sealing o-ring) with respect to which we
measured the position of the illuminating spot. A rigid displacement along
$x$ yields mostly a horizontal shift of the results shown in
Fig. \ref{fig:p} and that can bring them into closer agreement.
